데이터 분석가의 R 패키지 개발 도전기

### 2021-09-17 draft.Rmd
수정 - typo

```{r book, echo = FALSE, fig.cap="데이터미아닝 기법과 응용 / 한나래출판사 / 전치혁 저", out.height='400px', fig.align='center'}
knitr::include_graphics("images/book-cover.jpg")
```

>>>>

```{r book, echo = FALSE, fig.cap="데이터마이닝 기법과 응용 / 한나래출판사 / 전치혁 저", out.height='400px', fig.align='center'}
knitr::include_graphics("images/book-cover.jpg")
```
